Revisiting `Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation

### 2023-05-16 analysis/quarto/paper.tex
rewriting

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\journal{Journal of Behavioral and Experimental Economics}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Growth and inequality in public good provision --- an extended replication},
  pdfauthor={Hauke Roggenkamp},
  pdfkeywords={Replication study, Non-convenience sample, Open
science, Dynamic public good game, Online experiment, Generalizability},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Growth and inequality in public good provision --- an extended
replication}
\author[1,2]{Hauke Roggenkamp%
%
}
 \ead{hauke.roggenkamp@unisg.ch}

@@

\begin{abstract}
You can find the most recent version of this paper
\href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.pdf}{here}.
The abstract follows at later point.
\end{abstract}

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

Today's actions are tomorrow's result. There are many settings in which
current decisions affect future outcomes and with it, future decision
spaces. Opting for environmental friendly policies today not only
reduces carbon dioxide omissions immediately but also helps us to reach
the Paris climate targets tomorrow. Deferring these policies, may not
necessarily prevent us from reaching these targets, but it makes it more
difficult in the future. Hence, today's actions (or the omission
thereof) not only affect intermediate outcomes but also the number of
paths one can choose to reach certain goals.

Standard public good games---although often intended to inform climate
policies\footnote{See \citet[p.~1]{GKLS2020} for numerous references.}---miss
these temporal interdependencies simply because participants have the
same set of actions in each period. Accordingly, participants' actions
in a given period do not affect their number of actions in subsequent
periods. A game implemented by Gächter, Mengel, Tsakas \& Vostroknutov
\citeyearpar{GMTV2017} (hereafter, GMTV) as well as Stefan Große (2011,
unpublished) incorporated interdependencies into a \emph{dynamic} public
good game. Here, participants' actions in a given period affect their
number of actions in subsequent periods. Because there is surprisingly
little experimental research on these interdependencies\footnote{One
  exemption are \citet{Moser2019}, who built on GMTV's design do
  investigate leadership.}, I replicated one of their treatments.

\citet{GKLS2020} find that standard public good games do not generalize
to real-world climate action. Because the dynamic setting has a more
realistic property, one wonders whether it is better suited to inform
public policy. To answer this question, I ran the experiment with
different samples\footnote{GMTV ran their experiments with students in
  Nottingham, England.} online, that is, with participants who make
their decisions in an environment whcih is more natural than the lab. In
addition, I observed the participants' behavior in voluntary climate
actions (VCA). This yielded a setting similar to \citet{GKLS2020}'s
which allows me to analyze how behavior in the abstract game translates
into real-world action across samples.

\citet{AGM2018} conducted public good games in the lab and on MTurk to
draw lessons from online experimentation. This study extends this
literature \citep[see also][]{GoodmanPaolacci2017} by focusing on a
completely inexperienced sample that has not been exposed to interactive
experiments before. This required me to design a robust (and thus, more
complex) software to minimize attrition. In exchange, the online setting
allowed me to also collect paradata to assess the fluency and
feasibility of the experiment. This article reports on both topics: the
robust design as well as the feasibility.

Taken together, this study makes three contributions. First, it
replicates parts of GMTV's original experiment and highlights the
importance of pure replications. Second, it shows that logistically
complex online experiments are feasible for samples other than students
or clickworkers. Third, it shows that findings from abstract games do
not generalize well and even worse with the representative sample. After
reporting the methods, this paper is organized along these findings.

@@

In the terminology of \citet{Hamermesh2007}, I ran both a \emph{pure} as
well as a \emph{scientific replication}\footnote{\citet{Parsons2022} use
  the term of a \emph{conceptual replication} which means the same.} of
one treatment of GMTV's dynamic public good game. The pure replication
re-analyzes the original data.
\protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
\href{}{errors I identified} in the original paper. The scientific
replication, where I utilize a different sample drawn from a different
population in a different situation, is described in the following
sections.

@@

@@

What makes the game \emph{dynamic}? Instead of receiving fresh
endowments every period, participants received one endowment only at the
beginning of the first period. A participant's endowment in the second
period is the wealth he or she accumulated in the first period. A
participant's endowment in the third period is the wealth he or she
accumulated in the first two periods. And so on. Hence, a decision in
one period has consequences on future endowments and, ultimately, growth
paths. For this reason, the game is described as a \emph{dynamic} public
good game

@@

Like GMTV we employ a real giving task after the abstract game. In
contrast to GMTV and like \citet{GKLS2020}, we employed a VCA, where
they could donate any amount their earnings to offset carbon dioxide
(that is, retirine emission permits from the EU ETS).\footnote{Importantly,
  \citet{GKLS2020} made the VCA decision with a fresh endowment
  \emph{before} they played the abstract game. I deviate from their
  procedure to match GMTV's procedure.} To ensure that each participant
had the same basic level of information about the impact of their
decision, I provided some basic information about the mechanism. The
information also highlighted that the mitigation came into operation on
a European level. Finally, I informed the participants that the
documentation of individual and aggregate contributions were to be
posted immediately after the experiments online. To avoid privacy or
social image concerns, participants learned their unique and random IDs,
which they needed to identify their individual contributions. The
document certified that their contributions have been used to offset
\href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
tons} of carbon dioxide emissions.

\hypertarget{sec-sample}{%
\subsection{Sample}\label{sec-sample}}

@@

At the time I conducted the experiment, the more representative sample
was not familiar with interactive experiments. In fact, I ran the first
interactive group experiment with this sample. The students, in
contrast, were used to this kind of experiments. Recruiting them, I
excluded those who have participated in a public goods game before. As a
consequence, nonnaiveté is unlikely to affect the validity of the
experiment \citep[ p.~204]{GoodmanPaolacci2017}.

Throughout this paper, I will compare results of my experiment with the
results of GMTV's NOPUNISH 10 Period treatments. I am thus, referring to
three different samples utilized at two points in time: the University
of Nottingham's students (in late 2012), Hamburg's citizens and the
University Hamburg's students (both in July 2021).
Table~\ref{tbl-sample-properties} shows how they compare with respect to
a few properties.

\hypertarget{tbl-sample-properties}{}
\begin{table}[!htbp] \centering 
  \caption{\label{tbl-sample-properties}Sample Properties } 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
 & Female & Age & Trust & Meritocracy & Government & Equality \\ 
\hline \\[-1.8ex] 
 Hamburg Citizens & 0.48$^{***}$ & 47.58$^{***}$ & 3.90$^{***}$ & 3.79$^{***}$ & 3.44$^{***}$ & 4.17$^{***}$ \\ 
  & (0.07) & (1.21) & (0.19) & (0.21) & (0.19) & (0.23) \\ 
  & & & & & & \\ 
 Hamburg Students & 0.08 & $-$21.41$^{***}$ & $-$0.58$^{**}$ & 0.23 & 0.71$^{***}$ & 0.12 \\ 
  & (0.09) & (1.63) & (0.25) & (0.28) & (0.26) & (0.30) \\ 
  & & & & & & \\ 
 Nottingham Students & $-$0.10 & $-$15.85$^{***}$ & $-$0.03 & 1.65$^{***}$ & 0.87$^{***}$ & $-$0.35 \\ 
  & (0.09) & (1.52) & (0.23) & (0.26) & (0.24) & (0.28) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 208 & 208 & 208 & 208 & 208 & 208 \\ 
R$^{2}$ & 0.02 & 0.47 & 0.04 & 0.20 & 0.06 & 0.02 \\ 
Residual Std. Error & 0.50 & 8.75 & 1.35 & 1.52 & 1.40 & 1.63 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

Describe sample properties here.

@@

I chose oTree \citep{oTree} to implement the experiment because it is
open-source, well documented and very flexible. Its
\href{https://getbootstrap.com/}{Bootstrap} (a powerful frontend
toolkit) integration allowed me to make the graphical user interface
interactive, appealing and easy to navigate. The
\href{https://www.highcharts.com/}{Highcharts library} made it easy to
visualize results and to communicate dynamics. Insofar, oTree served a
good tool to enhance the participants' user experience and thus, to make
dropouts less likely. Furthermore, the oTree code snippets made it
possible to handle dropouts.

@@

Participants entered the experiment at appointed times remotely from
home. They first saw a welcome screen. After agreeing to the privacy
policy, they could proceed to the instructions individually. Having read
these instructions, each participant has also seen a demo-screen
explaining the user interface. Before proceeding, they had to answer six
comprehension questions correctly. Subsequently, they saw a waiting
screen until they could be matched with three other participants, who
have answered the comprehension questions correctly. Once matched, they
were exposed to the decision screen over ten periods. At the end of the
last period, participants saw results of all periods. Subsequently, they
made their VCA decision, before I elicited risk preferences
\citep{HoltLaury2002} and finished with GMTV's questionnaire.

While I tried to stick to GMTV's protocol as close as possible, I
deviated in a few aspects. First, the instructions were German and also
covered topics inherent to the online setting (dropouts and bots, for
instance). Second, I used another software (oTree instead of zTree).
Third, GMTV gave participants the opportunity to donate to \emph{Doctors
without Borders} whereas we offered carbon dioxide offsets. Fourth, the
graphical user interface looked different.

@@

\hypertarget{sec-registration}{%
\subsection{Pre-registration}\label{sec-registration}}

Parts of the analyses were pre-registered in the American Economic
Association's RCT Registry \citep{preregistration}. In addition, I
pre-registered the exact analyses I planned to run when I designed
designed the experiment on
\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
  to run the code, you need to executed the .Rmd files in this
  repository in the order that is indicated by its file names.}. GitHub
is a website and cloud-based service where developers---and researchers
alike---can store and manage their code. The service is based on
Git\footnote{Git is a specific open-source version control system
  developed in 2005.} and designed for version control. Importantly,
changes are timestamped and can be tracked. Moreover, one can create
branches, that is, duplicates of code -- either to work collaborative or
to archive a certain state. Accordingly, I archived my analyses scripts
and created a
\href{https://github.com/Howquez/coopUncertainty/tree/July21Replication}{branch}
a few days \emph{before} we collected data.

The analysis that makes the most sense now that I have collected the
data is a little different though: Because the more representative
subject pool was exhausted earlier than expected, I recruited students
unwantedly and changed parts of the scripts.\footnote{The source code of
  this document contains the analysis and can be found
  \href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}{here}:
  https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}
However, because the originally planned analysis code is archived and
reproducible, these changes are transparent and easy to assess.

@@

First, I ask whether the samples differ with respect to their initial
contributions to the public good. Is our replication sample more
pro-social than the original sample? Figure~\ref{fig-first-round}
reveals that it is not. The distributions of both samples look fairly
similar. Both samples contributed 10 tokens, that is, 50\% of their
endowments on average (median and mean).\footnote{The two-sided rank sum
  test (comparing differences between samples) yields a p-Value of
  0.3926 for the mean contribution in first round of the game.}
Moreover, both samples' initial contributions resemble initial
contributions participants usually make in the standard game with
partner matching.\footnote{See Figure 3B in \citet{fehrgaechter2000}
  (p.989), for instance.} However, in the dynamic game presented here,
we are particularly interested in the subsequent periods because
differences add up exponentially. Do the two groups remain similar over
the course of time?

{\centering \includegraphics{paper_files/figure-pdf/fig-first-round-1.pdf}

\caption{\label{fig-first-round}Individual contributions to the dynamic
public good in the first period}

In particular, do the two samples' contributions follow the same path
over the 10 periods they played? The answer is \emph{no}.
Figure~\ref{fig-share-of-contributions} illustrates that the samples
make similar contributions at the beginning and the end of the game but
behave differently in between. More precisely, the left panel--depicting
the average contributions in absolute terms--shows that the original
sample contributed substantially more than the replication sample
\emph{in all but the first and last period}. For this reason, the
original sample's behavior differs from the replication sample's
behavior in two aspects: it contributes more and exhibits a considerable
drop in the last period (whereas the replication sample's contributions
flatten).

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\journal{Journal of Behavioral and Experimental Economics}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Revisiting `Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation},
  pdfauthor={Hauke Roggenkamp},
  pdfkeywords={Replication study, Non-convenience sample, Open
science, Dynamic public good game, Online experiment, Generalizability},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Revisiting `Growth and Inequality in Public Good Provision'
---Reproducing and Generalizing Through Inconvenient Online
Experimentation}
\author[1,2]{Hauke Roggenkamp%
%
}
 \ead{hauke.roggenkamp@unisg.ch}

@@

\begin{abstract}
I revisit the dynamic public good game by Gächter et al.~(2017)
developed to study cooperation under dynamic interdependencies.
Collecting data from both students and a general population sample, I
not only reproduce some of the author's original observations but also
test the game's generalizability. Appending a charitable dictator game,
I find no correlations between behavior in the abstract game and the
charitable context. This applies to students and the general population
sample alike. Studying inexperiend general population samples raises
methodological challenges with respect to fatigue and dropouts. This
paper approaches them and provides simple solutions to run relieable
interactive experiments online.

You can find the most recent version of this paper
\href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.pdf}{here}.
\end{abstract}

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

Today's actions are tomorrow's result. There are many settings in which
current decisions affect future outcomes and with it, future decision
spaces. Opting for environmental friendly policies today not only
reduces carbon dioxide omissions immediately but also helps us to reach
the Paris climate targets tomorrow. Deferring these policies, may not
necessarily prevent us from reaching these targets, but it makes it more
difficult in the future. Hence, today's actions (or the omission
thereof) not only affect intermediate outcomes but also the number of
paths one can choose to reach certain goals. This apllies especially to
carbon dioxide emissions where its current stock will last for well over
a millennium \citep{Inman2008, CalzolariEtAl2018}.

Public good games---although often intended to inform climate policies
(e.g. \citet{MilinskiEtAl2006}, \citet{TavoniEtAl2011},
\citet{Hauser2014}, \citet{BrickEtAl2015}, \citet{GomezEtAl2018},
\citet{CalzolariEtAl2018}, \citet{CookEtAl2019})---miss these temporal
interdependencies simply because participants have the same set of
actions in each period. Accordingly, participants' actions in a given
period do not affect their number of actions in subsequent periods. A
game designed by Gächter, Mengel, Tsakas \& Vostroknutov
\citeyearpar{GMTV2017} (hereafter, GMTV) as well as Stefan Große (2011,
unpublished) incorporated interdependencies into a \emph{dynamic} public
good game. Here, participants' actions in a given period affect their
number of actions in subsequent periods. Because there is surprisingly
little experimental research on these interdependencies\footnote{One
  exemption are \citet{Moser2019}, who built on GMTV's design to
  investigate leadership.}, I reproduced one of their treatments to
compare dynamics across samples.

\citet{GKLS2020} find that standard public good games do not generalize
well to real-world climate action. They also find that generalizability
depends on structural resemblance of the public goods game with the
context of climate change mitigation. Greater resemblance improves
generalizability. Because GMTV's dynamic setting has a more realistic
property---namely, interdependencies---one wonders whether it is better
suited to inform public policy. To approach this question, I ran the
experiment with different samples\footnote{GMTV ran their experiments
  with students in Nottingham, England.} and observed the participants'
behavior in voluntary climate actions (VCA). This yielded a setting
similar to \citet{GKLS2020}'s which allows me to analyze how behavior in
the abstract game translates into real-world action across samples.

The VCA is a (charitable) dictator games where each participant is a
dictator dividing her budget between herself and some organization
linked to the reduction of CO2 emissions. \citet{EckelGrossman1996} were
the first to implement a charitable dictator game observing
contributions of 30\% of the endowments. Like \citet{GKLS2020},
\citet{CarpenterEtAl2008} report that students make lower contributions
to charity than community members.

\citet{AGM2018} conducted public good games in the lab and on MTurk to
draw lessons from online experimentation. This study extends this
literature \citep[see also][ \citet{AmirEtAl2012}]{GoodmanPaolacci2017}
by focusing on a completely inexperienced sample that has not been
exposed to interactive experiments before. This required me to design a
robust (and thus, more complex) software to minimize attrition. In
exchange, the online setting allowed me to also collect paradata to
assess the fluency and feasibility of the experiment. This article
reports on both topics: the robust design as well as the feasibility.

Taken together, this study makes three contributions. First, it
replicates parts of GMTV's original experiment and highlights the
importance of pure replications. Second, it shows that logistically
complex online experiments are feasible for samples other than students
or clickworkers. Third, this paper supports critics arguing that
findings from abstract games do not generalize well---not even with a
more representative sample. After reporting the methods, this paper is
organized along these findings.

\hypertarget{transparency}{%
\section{Transparency}\label{transparency}}

Well before credibility crises comprised a variety disciplines,
\citet[p.~2]{bemwriting} indirectly conceded discrepancies between fuzzy
research processes and the polished article that results from it:

\begin{quote}
\emph{``There are two possible articles you can write: (a) the article
you planned to write when you designed your study or (b) the article
that makes the most sense now that you have seen the results. They are
rarely the same, and the correct answer is (b).''}
\end{quote}

Now, 20 years later, we accustom ourselves with mechanisms designed to
unravel the fuzzy back-and-forth between exploratory and confirmatory
research. Prominently, pre-registrations were established to tie the
researchers' hands when doing confirmatory research--reducing observable
discrepancies between (a) and (b). Today, researchers can not only
choose where to pre-register but also decide about the level of detail
they provide. More severely, nothing stops researchers from
pre-registering multiple hypotheses opposing each other (see e.g.
\citet{SimmonsEtAl2021} and \citet{PhamEtAl2021} for a discussion).

\citet{WaldronAllen2022} report a wide variety of depth of
pre-registrations in the field of Neuropsychopharmacology and document
that the label \emph{`pre-registration'} can be obtained with minimal
effort. In absence of transparency and scrutiny pre-registrations run
into danger to miss the target of making science more credible. Even
more so, they may have adverse effects as the label
\emph{`pre-registered'} becomes cheap (too) to acquire.

Discussing the costs and benefits of pre-registrations,
\citet{Olken2015} stresses the uncertainty of research processes and
promotes moderate approaches. As \citet{WaldronAllen2022}, he argues
that pre-registrations not necessarily eliminate flexibility. These
`moderate' or `flexible' approaches require transparency to reduce
concerns of \emph{`data-mining'} \citep[ p.~61]{Olken2015} by showing
(a) the analyses I planned to run, (b) the analysis that made most sense
after collecting the data and the transition from (a) to (b). Because
this is neither incentivized nor easy to verify, we need tools that make
transparency convenient to establish and to scrutinize. I propose
version control (such as Git) as one such tool and illustrate its
application on this paper: GitHub is a website and cloud-based service
where developers---and researchers alike---can store and manage their
code. The service is based on Git\footnote{Git is a specific open-source
  version control system developed in 2005.} and designed for version
control. Importantly, changes are time-stamped and can be tracked.
Moreover, one can create branches, that is, duplicates of code -- either
to work collaborative or to archive a certain state.

To sum up, pre-registrations alone are necessary but not sufficient to
restore the credibility in experimental sciences. Pre-registrations must
come with additional emphasis on transparency covering the whole
research process as well as with a higher level of scrutiny that looks
beyond mere labels.

In fact, the experiment reported in this article qualifies for the label
\emph{`pre-registered'} at a first glance: Parts of the analyses were
pre-registered in the American Economic Association's RCT Registry
\citep{preregistration}. In addition, I pre-registered the exact
analyses I planned to run when I designed the experiment on
\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
  to run the code, you need to executed the .Rmd files in this
  repository in the order that is indicated by its file names.}.

The analysis that made the most sense after having collected the data is
a little different though: Because the more representative subject pool
was exhausted earlier than expected, I recruited students which opened
up a new research direction: assessing generalizability. Hence, this
article combines both confirmatory as well as exploratory research.

Accordingly, I changed many of the analysis scripts.\footnote{The source
  code of this document contains the analysis and can be found
  \href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}{here}:
  https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}
However, because the originally planned analysis code is archived and
reproducible, these changes are transparent and easy to assess,
showcasing (a), (b) and the transition from (a) to (b).

@@

In the terminology of \citet{Hamermesh2007}, I ran both a \emph{pure} as
well as a \emph{scientific} reproduction\footnote{\citet{Parsons2022}
  use the term of a \emph{conceptual replication} which means the same.}
of one treatment of GMTV's dynamic public good game. The pure
reproduction re-analyzes the original data.
\protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
\href{}{errors I identified} in the original paper. The scientific
replication, where I utilize a different sample drawn from a different
population in a different situation, is described in the following
sections.

@@

The design builds on the workhorse model \citet[p.301]{Zelmer2003}
describes in her meta-analysis, where

\begin{quote}
\emph{``subjects are divided into groups and play the same game for a
finite number of periods. Each period, every subject is endowed with an
income {[}\ldots{]} The subject must then divide this income between a
contribution to a private account {[}\ldots{]} that yields a constant
return to themselves only and a contribution to a public account
{[}\ldots{]} where consumption benefits accrue to all group members. At
the end of each period, subjects typically learn the aggregate
contribution to the public good by all members of their group and their
earnings for the period.''}
\end{quote}

Considering the design, the only differences between such a
\emph{static} game and GMTV's design are \emph{dynamics}: Instead of
receiving fresh endowments every period, participants receive one
endowment only at the beginning of the first period. A participant's
endowment in the second period is the wealth she accumulated in the
first period. A participant's endowment in the third period is the
wealth she accumulated in the first two periods. And so on. Hence, a
decision in one period has consequences on future endowments and,
ultimately, growth paths. For this reason, the game is described as a
\emph{dynamic} public good game.

@@

@@

Like GMTV we employ a real giving task after the abstract game. In
contrast to GMTV and like \citet{GKLS2020}, we employed a VCA, where
participants could donate any amount their earnings to offset carbon
dioxide (that is, retire emission permits from the EU ETS).\footnote{Importantly,
  \citet{GKLS2020} made the VCA decision with a fresh endowment
  \emph{before} they played the abstract game. I deviate from their
  procedure to match GMTV's procedure.} To ensure that each participant
had the same basic level of information about the impact of their
decision, I provided some basic information about the mechanism. The
information also highlighted that the mitigation came into operation on
a European level. Finally, I informed the participants that the
documentation of individual and aggregate contributions were to be
posted immediately after the concluding the sessions online. To avoid
privacy or social image concerns, participants learned their unique and
random IDs, which they needed to identify their individual
contributions. The document certified that their contributions have been
used to offset
\href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
tons} of carbon dioxide emissions.

\hypertarget{sec-sample}{%
\subsection{Recruitment and Sample Characteristics}\label{sec-sample}}

@@

At the time I conducted the experiment, the more representative sample
was not familiar with interactive experiments. In fact, I ran the first
interactive group experiment with this sample. The students, in
contrast, were used to single-player experiments. Recruiting them, I
excluded those who have participated in interactive experiments such as
public goods games before, to keep the two distinct subject pools
comparable in terms of their experience. As a consequence, nonnaiveté is
unlikely to affect the validity of the experiment \citep[
p.~204]{GoodmanPaolacci2017}.

Throughout this paper, I will compare results of my experiment with the
results of GMTV's NOPUNISH 10 Period treatments. I am thus, referring to
three different samples utilized at two points in time: the University
of Nottingham's students (in late 2012), Hamburg's citizens and the
University Hamburg's students (both in July 2021).
Table~\ref{tbl-sample-properties} gives an overview.

\hypertarget{tbl-sample-properties}{}
\begin{table}[!htbp] \centering \renewcommand*{\arraystretch}{1.1}\caption{\label{tbl-sample-properties}Sample Properties }\resizebox{\textwidth}{!}{
\begin{tabular}{lrrrrrrrrrl}
\hline
\hline
sample & \multicolumn{3}{c}{Hamburg Citizens} & \multicolumn{3}{c}{Hamburg Students} & \multicolumn{3}{c}{Nottingham Students} &   \\ 
 Variable & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Test} \\ 
\hline
Age & 52 & 48 & 15 & 64 & 26 & 7.6 & 92 & 33 & 2.6 & F$=88.98^{***}$ \\ 
Female & 52 & 0.48 & 0.5 & 64 & 0.56 & 0.5 & 92 & 0.38 & 0.49 & F$=2.596^{*}$ \\ 
Switching Row & 20 & 6.6 & 2.6 & 58 & 6 & 2 & 87 & 6.4 & 1.3 & F$=1.406^{}$\\ 
\hline
\hline
\multicolumn{11}{l}{Statistical significance markers: * p<0.1; ** p<0.05; *** p<0.01}\\ 
\end{tabular}
}
\end{table}

Overall, I recruited 116 participants for the experiment. The three
samples differ significantly with respect to their age. The non-student
sample is more diverse compared to the two student samples.

@@

I chose oTree \citep{oTree} to implement the experiment because it is
open-source, well documented and very flexible. Its
\href{https://getbootstrap.com/}{Bootstrap} (a powerful frontend
toolkit) integration allowed me to make the graphical user interface
interactive, appealing and easy to navigate. The
\href{https://www.highcharts.com/}{Highcharts library} made it easy to
visualize results and to communicate dynamics. Insofar, oTree served a
good tool to enhance the participants' user experience and thus, to make
dropouts less likely.

@@

Participants entered the experiment at appointed times remotely from
home. They first saw a welcome screen. After agreeing to the privacy
policy, they could proceed to the instructions individually. Having read
these instructions, each participant has also seen a demo-screen
explaining the user interface. Before proceeding, they had to answer six
comprehension questions correctly to avoid confusion in later stages
\citep{FerraroVossler2010}. Subsequently, they saw a waiting screen
until they could be matched with three other participants, who have
answered the comprehension questions correctly. Once matched, they were
exposed to the decision screen over ten periods. At the end of the last
period, participants saw results of all periods. Subsequently, they made
their VCA decision, before I elicited risk preferences
\citep{HoltLaury2002} and finished with GMTV's questionnaire.

While I stuck to GMTV's protocol as close as possible, I deviated in a
few aspects. First, the instructions were German and also covered topics
inherent to the online setting (dropouts and bots, for instance).
Second, I used another software (oTree instead of zTree) which also
affected the graphical user interface participants were exposed to.
Third, GMTV gave participants the opportunity to donate to \emph{Doctors
without Borders} whereas we offered carbon dioxide offsets.

@@

@@

First, I ask whether the samples differ with respect to their initial
contributions to the public good. Is the replication sample (consisting
of both students and non-students) more pro-social than the original
sample? A two-sided rank sum test reveals that it is not (p=0.3926).
Both samples contributed 10 tokens, that is, 50\% of their endowments on
average (median and mean). Moreover, both samples' initial contributions
resemble initial contributions participants usually make in the static
game with partner matching.\footnote{See Figure 3B in
  \citet[p.989]{fehrgaechter2000}, for instance.} However, in the
dynamic game presented here, we are particularly interested in the
subsequent periods because differences add up exponentially. Do the two
groups remain similar over the course of time?

In particular, do the two samples' contributions follow the same path
over the 10 periods they played? The answer is \emph{no}.
Figure~\ref{fig-share-of-contributions} illustrates that the samples
make similar contributions at the beginning and the end of the game but
behave differently in between. More precisely, the left panel--depicting
the average contributions in absolute terms--shows that the original
sample contributed more than the replication sample \emph{in all but the
first and last period}.\footnote{In period five, this difference is
  significant: a two-sided rank sum test yields p=0.0486.} For this
reason, the original sample's behavior differs from the replication
sample's behavior in two aspects: it contributes more and exhibits a
considerable drop in the last period (whereas the replication sample's
contributions flatten).

Note that increasing contributions over time imply increasing endowments
over time. Hence, absolute contributions do not tell much about the
willingness to cooperate. For this reason, the right panel in
Figure~\ref{fig-share-of-contributions} shows the average \emph{share of
endowments contributed} over time. Both samples exhibit a similar
pattern: their share of endowments contributed declined and did not
stabilize. However, both samples also differ with respect to one aspect:
the replication sample's share of contributions declines faster. This is
mirrored by a two-sided rank sum test which is only significant at a
five percent level in periods three and four.
